---
title: "Site evaluation"
author:
  - name: Alke Voskamp
date: "2021-08-12"
output: html_document
params: 
    set_weights_table: NA
    plot_sites: NA
    weighing: NA
---

```{r setup, include=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sites evaluated based on macroecological indicators
Results of the site evaluation based on the weighted objectives. The percentage table shows the 
allocated percentages for each objective that resulted in the site ranking. 

```{r set_weights_table, echo=FALSE}
kable(params$set_weights_table)
```

The map shows the location of the top protected areas according to the applied weighting.
```{r plot_sites, echo=FALSE, warning = FALSE}
plot(params$plot_sites)
```

The data table shows the ranking of the protected areas (PAs) based on the allocated weights. The values
shown under the individual conservation objectives are the scaled scores for each PA.
```{r weighting, echo=FALSE}
kable(params$weighing[1:30,])
```


## How to interpret the evaluation results
The different objectives included have varying error margins and can lead to uncertainty around the
allocated ranks. Ranks resulting from an evaluation that include the biodiversity, climate protection
or size objective only are more certain than ranks that result from an evaluation that included also the 
wilderness objective. The highest uncertainty in the allocated ranks comes from the climate stability and
land-use objectives.
The resulting ranking is supposed to give an overview which sites score highly under the chosen objectives 
on a global or realm scale. They cannot replace a thorough on the ground assessment of the sites but help
to narrow the number candidate sites for further evaluation down.
